Hydras \& Co.

### 2024-01-08 doc/chapter-primrec.tex
small corrections

\begin{remark}
In the following snippet,  \emph{Alectryon}'s \texttt{Latex} generator  prints the \emph{local definition} of $x$ (as the maximum of $2$ and $m$) as a simple \emph{declaration} \texttt{x: nat}.
Thus the proof script is correct, but the three last sub-goals are not correctly displayed, since 
they do not show how the inequalities $2\leq x$ and $m \leq x$ could be inferred by \texttt{lia}.
\end{remark}

@@

\begin{remark}
It is easy to prove that any unary function which dominates \texttt{fun n => Ack n n} fails to be primitive recursive. To this end, we use an instance of \texttt{majorAnyPR} dealing with unary functions.

>>>>

\begin{remark}
In the following snippet,  some versions \emph{Alectryon}'s \texttt{Latex} generator  print the \emph{local definition} of $x$ (as the maximum of $2$ and $m$) as a simple \emph{declaration} \texttt{x: nat}.
Thus the proof script is correct, but the three last sub-goals are not correctly displayed, since 
they do not show how the inequalities $2\leq x$ and $m \leq x$ could be inferred by \texttt{lia}.

A correct goal display can be obtained with
\href{https://github.com/Casteran/alectryonFix}{this fork}.
\end{remark}

@@

\begin{remark}
It is easy to prove that any unary function which dominates (\texttt{fun n => Ack n n}) fails to be primitive recursive. To this end, we use an instance of \texttt{majorAnyPR} dealing with unary functions.
